Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update table and figure references in results

\section{Results, Metrics}

@@

@@

The area cover of the OSM dataset in relation to the SLU dataset was estimated to 98.18\%.

Building matching statistics:

@@

% Bar plot positional accuracy

@@

% Bar plot turning functions

@@

\subsection{Road collision statistics}

After collision correction:

>>>>

\section{Results and metrics}

For the secondary study, the average positional accuracy per building was calculated to roughly 2.06 meters, and this will be taken as an estaimate of the positional accuracy of the OSM dataset.
Table \ref{table:positional-accuracy} shows the estimate in positional accuracy that was obtained from the study.
Figure \ref{fig:bar-plot-positional-accuracy} shows the positional accuracies measured per building as a frequency diagram.

\subsection{Road collision study}

For the primary collision study.

Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features before road extrusion, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.

@@

Table \ref{table:num-of-buildings} shows the building coverage of the OSM and SLU datasets in terms of the number of buildings and their total area.
Table \ref{table:num-of-buildings-percent} shows the building coverage of both datasets as perentages.
The area cover of the OSM dataset in relation to the SLU dataset was estimated to 98.18\%. This will be taken as an estimate of the completeness of the OSM dataset.

@@

\subsection{Building matching statistics}

Table \ref{table:building-matching} shows how many of the OSM to SLU building matches were found in each category of 1:1, 1:n and 1:0 matches.

@@

@@

Figure \ref{fig:bar-plot-similarity} shows the shape similarity measured per building as a frequency diagram.

@@
